A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-07-16 text/discussion.Rmd
update discussion of metastasis, add knott asparagine reference

The class-specific metastatic pathway enrichment we observe (in **table 2**) may
be a result of the pathways directly promoting metastatic phenotypes, or
alternatively that such mutations are more likely to turn metastatic because
they acquire a stronger or more complete oncogenic phenotype, since (again) we
don’t know the order in which they were acquired. The fact that most metastatic
enrichment is cluster-specific and has a tendency to overlap with
cluster-specific pathways from non-metastatic tumors of neighboring clusters
favors the latter explanation, and suggests a mechanism of complementarity in
which newly acquired mutations converge on a single deadly phenotype that
captures most or all of the critical features of end-stage cancer. If this is
the case, we speculate that once we discover the vulnerabilities of each cluster
we might also reasonably predict which pathways are susceptible to further
selection and therefore target them  therapeutically at the same time to prevent
further adaptation.

>>>>

We report that pathway enrichment across all classes (pooled) yielded generally
lower effect sizes and larger p-values than the cluster specific analysis,
suggesting that signal is diluted when the samples are analyzed this way, and
supporting the view that metastasis has class-specific requirements. It should
be noted, however, that in spite of this lack of global enrichment, some of the
cluster specific pathways reflect known metastatic associations, _e.g._ pathways
associated with asparagine and aspartate metabolism in class 10
[@knott_asparagus]. Since the number of metastatic tumors is relatively low this
part of our analysis is likely underpowered and subject to expanded analysis
with larger cohorts. Nonetheless, the class-specific metastatic pathway
enrichment we observe (in **table 2**) could be a result of the pathways
directly promoting metastatic phenotypes in these classes, or because they
acquire a stronger or more complete oncogenic phenotype, since (again) we don’t
know the order in which they were acquired in individual tumor samples. The fact
that most metastatic enrichment is cluster-specific and has a tendency to
overlap with cluster-specific pathways from non-metastatic tumors of neighboring
clusters favors the latter interpretation, and suggests a mechanism of
complementarity, in which newly acquired mutations result in similar classes
converging on a single deadly phenotype that captures most or all of the
critical features of end-stage cancer. If this is the case, once we discover the
requirements of each cluster with respect to metastasis we can target them
therapeutically and prevent further adaptation.
